Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-22 ICML2019/main.tex
update the experiments section

\paragraph{Experiments on Real Data Sets}
We use four data sets from UCI Machine Learning repository. Each data set contains 1 binary variable. By setting the prior distribution as $\betad(1,1)$, we 
\begin{figure}
\centering
\includegraphics[width=0.35\textwidth]{realdata.eps}
\caption{Accuracy on Real Data Sets, with $\epsilon = 1.0$}
\label{fig_vs_prior}
\end{figure}

>>>>

\paragraph{Experiments on Real Data Sets}
We use four real data sets from UCI Machine Learning repository\footnote{https://archive.ics.uci.edu/ml/datasets.html}. Each data set contains 1 binary variable, which applys our Beta-binomial model. By setting the prior distribution as $\betad(1,1)$, we apply our 5 private inference algorithms on them to derive the underlining distribution of these data. The first data set is the SHARING BIKE data, where $0$ means user use sharing bike at workday and $1$ stands for weekend. The second and third data set the THERAPY data, where $1$ means patient with disease is cured and $1$ means not. The forth data set is the BADGE data, $1$ means people with badge and $0$ means without badge.
\begin{figure}
\centering
\includegraphics[width=0.35\textwidth]{realdata.eps}
\caption{Accuracy on Real Data Sets, with $\epsilon = 1.0$}
\label{fig_vs_prior}
\end{figure}
